\documentclass[12pt,a4paper,twoside]{memoir}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\author{Robert James}
\title{Interfaces in the 2D Potts model}

\begin{document}
\begin{itemize}
	\item Introduction: Give basic idea of the project and its content. Describe (and give references to) other relevant work in the literature.
	\item Theory / Methodology: Necessary theoretical background or experimental methodology.
	\item Apparatus (if any): Description, design, construction. Materials used. Electronics and other devices purchased (giving type numbers etc).
	\item Results: General observations, data, tables, New theoretical calculations,etc.
	\item Discussion of Results: Analysis of results, graphs, etc., linking in with theory. Error analysis when appropriate.
	\item Conclusions and Suggestions for Future Work.
	\item Appendices: Computer programs etc.
	\item References: Papers, books, etc. Seek your supervisor’s guidance about the style of giving references.
	\item Acknowledgements: Help from workshop staff, technicians, fellow students, etc.

\end{itemize}

% begin abstract
\include{0-abstract/abstract.tex}
% end abstract

% begin Introduction
\include{1-Introduction/Introduction.tex}
% end Introduction

% begin Theory
\include{2-Theory/Theory.tex}
% end Theory

% begin Code
\include{3-Code/Code.tex}
% end Code

% begin Results
\include{4-Results/Results.tex}
% end Results

% begin DiscussionofResults
\include{5-DiscussionofResults/DiscussionofResults.tex}
% end DiscussionofResults

% begin Conclusions
\include{6-Conclusions/Conclusions.tex}
% end Conclusions

% begin Appendices
\include{7-Appendices/Appendices.tex}
% end Appendices

% begin References
\include{8-References/References.tex}
% end Referecnes

% begin Acknowledgments
\include{9-Acknowledgements/Acknowledgements.tex}
% end Acknowledgements

\end{document}
